Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-09-06 Manuscript Analyses/manuscript_analysis.Rmd
updated tables

All data processing and analyses were conducted using R Version 4.3.2.

@@

@@

# Removing Participant 323 from the dataset (missing demographic and cognitive data)

data <- data %>%
  dplyr::filter(id != 323)

demo <- demo %>%
  dplyr::filter(id != 323)

@@

>>>>

All data processing and analyses were conducted using R Version 4.4.1

@@

## Younger adult df
young_adult <- rio::import("cleaned_scored.csv") |>
  dplyr::select(-group_number)

@@

# Removing Participant 323 and 332 from the dataset (missing demographic and cognitive data)

data <- data %>%
  dplyr::filter(id != 323 & id != 332)

demo <- demo %>%
  dplyr::filter(id != 323 & id != 332)

@@

### Comparing Younger vs. Older Adults

#### Age-Corrected

The younger adult data comes from https://osf.io/y32qc/

older_adult <- pl_int |>
  dplyr::filter(type == "pretest") |>
  dplyr::select(id, ends_with("_c"), ends_with("_u"), best_win) |>
  dplyr::select(-c(fluid_cog_c, fluid_cog_u, pic_seq_c, pic_seq_u)) |>
  dplyr::rename(win = best_win) |>
  dplyr::mutate(group = "old") |>
  dplyr::filter()

young_adult <- young_adult |>
  dplyr::select(-c(age_in_years, win_l, win_r, fluid_cog_c, fluid_cog_u, pic_seq_c, pic_seq_u))

compare_df <- rbind(older_adult, young_adult)

compare_table_c <- compare_df %>%
  dplyr::select(id, ends_with("_c"), win, group) %>% 
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Words in Noise Threshold` = win
  ) %>%
  select(-id) %>% 
  tbl_summary(
    by = group,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

compare_table_c

#### Uncorrected Scores

compare_table_u <- compare_df %>%
  dplyr::select(id, ends_with("_u"), win, group) %>% 
  dplyr::rename(
    `Working Memory` = list_sort_u,
    `Inhibitory Control` = flanker_u,
    `Cognitive Flexibility` = card_sort_u,
    `Receptive Vocabulary` = vocab_u,
    `Processing Speed` = pattern_u,
    `Words in Noise Threshold` = win
  ) %>%
  select(-id) %>% 
  tbl_summary(
    by = group,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

compare_table_u
